Quantifying the ease of viral escape from broad and narrow antibodies to influenza hemagglutinin

### 2017-10-13 paper/manuscript.tex
Added a few comments as a reminder of what to mention
minor suggestions to second results section

\subsection*{Broad and narrow antibodies that neutralize influenza virus}
\comment{Juhye writes a draft of this section.}

@@

In order to compare the potencies of these antibodies, we completed GFP-based neutralization assays using wild-type A/WSN/1933 (H1N1) virus. 
Figure~\ref{fig:neutcurves} shows the neutralization curves for each antibody, and all six antibodies show similar potencies.
We chose to conduct the library selections with concentrations of antibodies that would neutralize nearly all wildtype viruses.

% (selection of escape mutants from S139/1 and C179 have been reported, but no reported escape mutants from FI6v3)

@@

>>>>

\subsection*{Broad and narrow antibodies that neutralize influenza virus}
We applied this approach to several broad antibodies that neutralize the A/WSN/1933 (H1N1) influenza virus strain.
For comparison, we also included several narrow strain-specific antibodies that we have characterized previously~\cite{doud2017complete}.
Two broad anti-stalk, one all one only group 1.
One anti receptor
The narrow ones.
The last concluding sentence of your paragraph is good.

@@

To choose appropriate concentrations of these antibodies, we performed neutralization assays using wild-type A/WSN/1933 (H1N1) virus. 
Figure~\ref{fig:neutcurves} shows the neutralization curves for each antibody, and all six antibodies show similar potencies.
We chose to conduct the library selections with concentrations of antibodies that would neutralize nearly all wildtype viruses (possibly add slightly more detail).

@@

% For S139/1, we see strong escape at three sites. These three sites were previously reported as sites of escape in selection experiments with S139/1 (cite Yoshida) G158N mutation introduces a potential glycosylation site
% The binding footprint of FI6v3 and C179 and the angle of approach of both antibodies is very similar (cite dreyfus). 
% For these two antibodies, we see selection for a few common escape mutations (S/T at site280, S at site 291, R at 47 / 48 (HA2), but also selection for distinct escape mutations (site 2, site 38, site 323, sites 42, 43)
